---
title: "Giant Seabass Tracking Project"
author: "Juliette Verstaen"
date: "4/16/2019"
output: pdf_document
toc: true
toc_depth: 2

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##1. Load Packages and Data
```{r}
library(tidyverse)
library(sf)
library(sp)
library(ggpubr)
library(readxl)
library(lubridate)
library(raster)
library(rworldmap)
library(ggplot2)
library(scales) 

```

**Necessary data format and notes**
Date and Time: yyyy-mm-dd hh:mm:ss
Station: SB-XX
Lat/long: Almost every station has 2-3 different lat/longs associated with it (although they are very very close). I didn't mess with this since its close enough. Some points on graphs are a little wonky because of this

I only kept in 5 columns: time stamp, transmitter, station name, lat, and long. Adding all the info for the other columns is not necessary for my analyze thus far, but if important into the future would need to be included here, and then renamed appropriatly in the code below.

Future fun stuff: Add temperature data to some of the graphs and maybe do some statistical testing to prove that the lower temps mean less likely to see seabass. Maybe find a threshold.

##1. Data
```{r}

detec1 <- read_excel("/seabass/data/detections_6_4_2019.xls")
detec2 <- read_excel("/seabass/data/detections_6_4_2019.xls")
###load in other data here as you get it and then add to the rbind code

detec <- rbind(detec1, detec2) %>%
  distinct()

#rename columns
names(detec) <- c("date_time", "transmitter", "station", "lat", "long")

#simplify transmitter name
detec <- detec %>%
  separate(transmitter, c("first", "second", "transmitter")) %>%
  dplyr::select(date_time, transmitter, station, long, lat) %>%
  filter( transmitter != "62806")

class(detec$date_time)
#needs to be in "POSIXct" "POSIXt" 

trans_counts <-detec %>%
  group_by(transmitter) %>%
  count(transmitter) %>%
  ungroup()

```

##2. Abacus graphs

**Seperate by fish and station**
```{r}

# 1 fish
f1_29792 <- detec %>%
  filter(transmitter == "29792")

#2 fish
f2_9712 <- detec %>%
  filter(transmitter == "9712")

#3 fish
f3_9714 <- detec %>%
  filter(transmitter == "9714")

#4 fish
f4_9716 <- detec %>%
  filter(transmitter == "9716")

#5 fish
f5_9718 <- detec %>%
  filter(transmitter == "9718")

```

**Plot abacus graphs**

*Fish 1: 29792*
```{r}

#1 fish
f1 <-ggplot(f1_29792, aes(x=date_time, y= station )) +
       geom_point(shape=15) +
       theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ggtitle("Transmitter #29792") +
   scale_x_datetime() +
  xlim(c(as.POSIXct('2018-08-31 00:00:00', format = "%Y-%m-%d %H:%M:%S"),
     as.POSIXct('2018-12-01 00:00:00', format = "%Y-%m-%d %H:%M:%S")))
  
f1

#first 9ish points are from the tracker being on the boat, so not including them in the graph
```

*Fish 2: 9712*
```{r}

#2 fish
f2 <-ggplot(f2_9712, aes(x=date_time, y= station )) +
       geom_point(shape=15) +
       theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
       scale_x_datetime() +
  ggtitle("Transmitter #9712")

f2

```



*Fish 3: 9714*
```{r}

#3 fish
f3 <-ggplot(f3_9714, aes(x=date_time, y= station )) +
       geom_point(shape=15) +
       theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
       scale_x_datetime() +
  ggtitle("Transmitter #9714")

f3

```


*Fish 4: 9716*
```{r}

#4 fish
f4 <-ggplot(f4_9716, aes(x=date_time, y= station )) +
       geom_point(shape=15) +
       theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
       scale_x_datetime() +
  ggtitle("Transmitter #9716")

f4

```

*Fish 5: 9718*
```{r}

#5 fish
f5 <-ggplot(f5_9718, aes(x=date_time, y= station )) +
       geom_point(shape=15) +
       theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
       scale_x_datetime() +
  ggtitle("Transmitter #9718")

f5

```

*All abacus graphs seperate*
```{r}

all_abacus <- ggarrange(f1, f2, f3,f4, f5 , 
          ncol = 2, nrow = 3)

#f3 only has one obsrvation

all_abacus
#ggsave("all_abacus.jpg", width=5, height=7, dpi=300)

```


*All fish on one abacus graph*
```{r}

all <-ggplot(detec) +
       geom_point(shape=15, aes(x=date_time, y= station, color= transmitter )) +
       theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
       scale_x_datetime() +
  ggtitle("All Fish")

all

```


Note: To zoom in on only one part of a graph when x-axis is date:
  xlim(c(as.POSIXct('2018-08-31 00:00:00', format = "%Y-%m-%d %H:%M:%S"),
     as.POSIXct('2018-12-01 00:00:00', format = "%Y-%m-%d %H:%M:%S")))

##3. Detection frequencies

###A. Histograms: Frequency detections/hour over time 

*the grouping I did should have worked but double check R logic behind it*

*Fish 1: 29792*
```{r}

##data wrangle

f1_hourly <- detec %>%
  filter(transmitter == "29792")%>%
  mutate(freq= 1) %>%
  separate(date_time, c("date", "time"), sep= " ") %>%
  separate(time, c("hour", "minute", "second"), sep = ":") %>%
  group_by(date, hour, transmitter, station, lat, long) %>%
  summarise(freq=sum(freq)) %>%
  mutate(minute= "00") %>%
  mutate(second= "00") %>%
  unite(time_1, minute, second, sep= ":")%>%
  unite(time, hour, time_1, sep = ":") %>%
  unite(date_time, date, time, sep = " ")

#changing classes for time and coordinates
f1_hourly$date_time <- as.POSIXct(f1_hourly$date_time, format="%Y-%m-%d %H:%M")
data(f1_hourly, package = "sp")
f1_hourly_sf <- st_as_sf(f1_hourly, coords= c("long","lat"), crs=4326)
f1_hourly_sp <- as(f1_hourly_sf, "Spatial")

f1_hist <- ggplot(data=f1_hourly, aes(x=date_time, y=freq)) +
   geom_bar(stat="identity", color="darkgreen")+
  theme_bw()+
  ggtitle("Detections/hour: 29792")
#  xlim(c(as.POSIXct('2018-08-31 00:00:00', format = "%Y-%m-%d %H:%M:%S"),
#     as.POSIXct('2018-12-01 00:00:00', format = "%Y-%m-%d %H:%M:%S")))

f1_hist


```


*Fish 2: 9712*
```{r}

##data wrangle

f2_hourly <- detec %>%
  filter(transmitter == "9712")%>%
  mutate(freq= 1) %>%
  separate(date_time, c("date", "time"), sep= " ") %>%
  separate(time, c("hour", "minute", "second"), sep = ":") %>%
  group_by(date, hour, transmitter, station, lat, long) %>%
  summarise(freq=sum(freq)) %>%
  mutate(minute= "00") %>%
  mutate(second= "00") %>%
  unite(time_1, minute, second, sep= ":")%>%
  unite(time, hour, time_1, sep = ":") %>%
  unite(date_time, date, time, sep = " ")

#changing classes for time and coordinates
f2_hourly$date_time <- as.POSIXct(f2_hourly$date_time, format="%Y-%m-%d %H:%M")
data(f2_hourly, package = "sp")
f2_hourly_sf <- st_as_sf(f2_hourly, coords= c("long","lat"), crs=4326)
f2_hourly_sp <- as(f2_hourly_sf, "Spatial")

f2_hist <- ggplot(data=f2_hourly, aes(x=date_time, y=freq)) +
   geom_bar(stat="identity", color="darkgreen")+
  theme_bw()+
  ggtitle("Detections/hour: 9712")
f2_hist

```


*Fish 3: 9714*
```{r}

##data wrangle

f3_hourly <- detec %>%
  filter(transmitter == "9714")%>%
  mutate(freq= 1) %>%
  separate(date_time, c("date", "time"), sep= " ") %>%
  separate(time, c("hour", "minute", "second"), sep = ":") %>%
  group_by(date, hour, transmitter, station, lat, long) %>%
  summarise(freq=sum(freq)) %>%
  mutate(minute= "00") %>%
  mutate(second= "00") %>%
  unite(time_1, minute, second, sep= ":")%>%
  unite(time, hour, time_1, sep = ":") %>%
  unite(date_time, date, time, sep = " ")

#changing classes for time and coordinates
f3_hourly$date_time <- as.POSIXct(f3_hourly$date_time, format="%Y-%m-%d %H:%M")
data(f3_hourly, package = "sp")
f3_hourly_sf <- st_as_sf(f3_hourly, coords= c("long","lat"), crs=4326)
f3_hourly_sp <- as(f3_hourly_sf, "Spatial")

f3_hist <- ggplot(data=f3_hourly, aes(x=date_time, y=freq)) +
   geom_bar(stat="identity", color="darkgreen")+
  theme_bw()+
  ggtitle("Detections/hour: 9714")
f3_hist

```


*Fish 4: 9716*
```{r}

##data wrangle

f4_hourly <- detec %>%
  filter(transmitter == "9716")%>%
  mutate(freq= 1) %>%
  separate(date_time, c("date", "time"), sep= " ") %>%
  separate(time, c("hour", "minute", "second"), sep = ":") %>%
  group_by(date, hour, transmitter, station, lat, long) %>%
  summarise(freq=sum(freq)) %>%
  mutate(minute= "00") %>%
  mutate(second= "00") %>%
  unite(time_1, minute, second, sep= ":")%>%
  unite(time, hour, time_1, sep = ":") %>%
  unite(date_time, date, time, sep = " ")

#changing classes for time and coordinates
f4_hourly$date_time <- as.POSIXct(f4_hourly$date_time, format="%Y-%m-%d %H:%M")
data(f4_hourly, package = "sp")
f4_hourly_sf <- st_as_sf(f4_hourly, coords= c("long","lat"), crs=4326)
f4_hourly_sp <- as(f4_hourly_sf, "Spatial")

f4_hist <- ggplot(data=f4_hourly, aes(x=date_time, y=freq)) +
   geom_bar(stat="identity", color="darkgreen")+
  theme_bw()+
  ggtitle("Detections/hour: 9716")
f4_hist

```


*Fish 5: 9718*
```{r}

##data wrangle

f5_hourly <- detec %>%
  filter(transmitter == "9718")%>%
  mutate(freq= 1) %>%
  separate(date_time, c("date", "time"), sep= " ") %>%
  separate(time, c("hour", "minute", "second"), sep = ":") %>%
  group_by(date, hour, transmitter, station, lat, long) %>%
  summarise(freq=sum(freq)) %>%
  mutate(minute= "00") %>%
  mutate(second= "00") %>%
  unite(time_1, minute, second, sep= ":")%>%
  unite(time, hour, time_1, sep = ":") %>%
  unite(date_time, date, time, sep = " ")

#changing classes for time and coordinates
f5_hourly$date_time <- as.POSIXct(f5_hourly$date_time, format="%Y-%m-%d %H:%M")
data(f5_hourly, package = "sp")
f5_hourly_sf <- st_as_sf(f5_hourly, coords= c("long","lat"), crs=4326)
f5_hourly_sp <- as(f5_hourly_sf, "Spatial")

f5_hist <- ggplot(data=f5_hourly, aes(x=date_time, y=freq)) +
   geom_bar(stat="identity", color="darkgreen")+
  theme_bw()+
  ggtitle("Detections/hour: 9718")
f5_hist

```

*All Frequency/Hour Histograms*
```{r}

all_hist <- ggarrange(f1_hist, f2_hist, f3_hist,f4_hist, f5_hist , 
          ncol = 2, nrow = 3)

#f3 only has one obsrvation

all_hist
#ggsave("all_hist.jpg", width=5, height=7, dpi=300)

```


Aggregated Frquency/hour 

```{r}

all_hourly <- detec %>%
  mutate(freq= 1) %>%
  separate(date_time, c("date", "time"), sep= " ") %>%
  separate(time, c("hour", "minute", "second"), sep = ":") %>%
  group_by(date, hour, transmitter, station, lat, long) %>%
  summarise(freq=sum(freq)) %>%
  mutate(minute= "00") %>%
  mutate(second= "00") %>%
  unite(time_1, minute, second, sep= ":")%>%
  unite(time, hour, time_1, sep = ":") %>%
  unite(date_time, date, time, sep = " ")

#changing classes for time and coordinates
all_hourly$date_time <- as.POSIXct(all_hourly$date_time, format="%Y-%m-%d %H:%M")
data(all_hourly, package = "sp")
all_hourly_sf <- st_as_sf(all_hourly, coords= c("long","lat"), crs=4326)
all_hourly_sp <- as(all_hourly_sf, "Spatial")

all_hist <- ggplot(data=all_hourly, aes(x=date_time, y=freq)) +
   geom_bar(stat="identity", color="darkgreen")+
  theme_bw()+
  ggtitle("All Detections/hour")
all_hist

```



###B. Spatial mapping of detection frequency at each station

Reading in CA shapefiles
```{r}

ca <- st_read(dsn = "data/ca_shape/CA", layer = "CA")
ca <- ca%>% 
  st_transform(4326)

```

Location GPS points for each reciever
```{r}

statGPS <- read_csv("data/StationGPS.csv")

#converting to spatial
data(statGPS, package = "sp")
statGPS_sf <- st_as_sf(statGPS, coords= c("long","lat"), crs=4326)
statGPS_sp <- as(statGPS_sf, "Spatial")


```

All Detections
```{r}

##data wrangle

all_freq <- detec %>%
  mutate(freq= 1) %>%
  group_by(station, lat, long) %>%
  summarise(freq=sum(freq)) %>%
  filter(freq != 1)

#converting to spatial
data(all_freq, package = "sp")
all_freq_sf <- st_as_sf(all_freq, coords= c("long","lat"), crs=4326)
all_freq_sp <- as(all_freq_sf, "Spatial")

#map dectections by frequency= color

all_freq_map <- ggplot(data = statGPS_sf) +
  geom_sf(color= "gray76")+
 geom_sf(data= all_freq_sf, aes(color = all_freq_sf$freq))+
  scale_colour_viridis_c() +
  geom_sf(data = ca, color = "darkgreen", fill = "darkgreen") +
  ggtitle("Most Frequented Receivers") +
  coord_sf(xlim = c(-119.01, -119.06), ylim = c(33.46, 33.495))+
  theme_bw()

all_freq_map

#ggsave("detec_station.jpg", width=5, height=7, dpi=300)

```

Unsure as to why some of the stations in the top right are not in the same exact location as the tracking signals.I created a csv file with just the stations so many the locations I pulled from the OG data file weren't right?

Fish 1 (29792) Detections
```{r}

f1_freq <- f1_29792 %>%
  mutate(freq= 1) %>%
  group_by(station, lat, long) %>%
  summarise(freq=sum(freq))

#converting to spatial
data(f1_freq, package = "sp")
f1_freq_sf <- st_as_sf(f1_freq, coords= c("long","lat"), crs=4326)
f1_freq_sp <- as(f1_freq_sf, "Spatial")

f1_freq_map <- ggplot(data = statGPS_sf) +
  geom_sf(color= "gray76")+
 geom_sf(data= f1_freq_sf, aes(color = f1_freq_sf$freq))+
  scale_colour_viridis_c() +
  geom_sf(data = ca, color = "darkgreen", fill = "darkgreen") +
  ggtitle("Detections f1(29792)") +
  coord_sf(xlim = c(-119.01, -119.06), ylim = c(33.46, 33.495))+
  theme_bw()


f1_freq_map

```
#note: have not removed the first day data where the transmitter was on the boat

Fish 2 (9712) Detections
```{r}

f2_freq <- f2_9712 %>%
  mutate(freq= 1) %>%
  group_by(station, lat, long) %>%
  summarise(freq=sum(freq))

#converting to spatial
data(f2_freq, package = "sp")
f2_freq_sf <- st_as_sf(f2_freq, coords= c("long","lat"), crs=4326)
f2_freq_sp <- as(f2_freq_sf, "Spatial")

f2_freq_map <- ggplot(data = statGPS_sf) +
  geom_sf(color= "gray76")+
 geom_sf(data= f2_freq_sf, aes(color = f2_freq_sf$freq))+
  scale_colour_viridis_c() +
  geom_sf(data = ca, color = "darkgreen", fill = "darkgreen") +
  ggtitle("Detections f2(9712)")+
  coord_sf(xlim = c(-119.01, -119.06), ylim = c(33.46, 33.495))+
  theme_bw()

f2_freq_map

```

Fish 3 (9714) Detections

```{r}

f3_freq <- f3_9714 %>%
  mutate(freq= 1) %>%
  group_by(station, lat, long) %>%
  summarise(freq=sum(freq))

#converting to spatial
data(f3_freq, package = "sp")
f3_freq_sf <- st_as_sf(f3_freq, coords= c("long","lat"), crs=4326)
f3_freq_sp <- as(f3_freq_sf, "Spatial")

f3_freq_map <- ggplot(data = statGPS_sf) +
  geom_sf(color= "gray76")+
 geom_sf(data= f3_freq_sf, aes(color = f3_freq_sf$freq))+
  scale_colour_viridis_c() +
  geom_sf(data = ca, color = "darkgreen", fill = "darkgreen") +
  ggtitle("Detections f3(9714)")+
  coord_sf(xlim = c(-119.01, -119.06), ylim = c(33.46, 33.495))+
  theme_bw()

f3_freq_map

```


Fish 4 (9716) Detections
```{r}

f4_freq <- f4_9716 %>%
  mutate(freq= 1) %>%
  group_by(station, lat, long) %>%
  summarise(freq=sum(freq))

#converting to spatial
data(f4_freq, package = "sp")
f4_freq_sf <- st_as_sf(f4_freq, coords= c("long","lat"), crs=4326)
f4_freq_sp <- as(f4_freq_sf, "Spatial")

f4_freq_map <- ggplot(data = statGPS_sf) +
  geom_sf(color= "gray76")+
 geom_sf(data= f4_freq_sf, aes(color = f4_freq_sf$freq))+
  scale_colour_viridis_c() +
  geom_sf(data = ca, color = "darkgreen", fill = "darkgreen") +
  ggtitle("Detections f4(9716)")+
  coord_sf(xlim = c(-119.01, -119.06), ylim = c(33.46, 33.495))+
  theme_bw()

f4_freq_map

```

Fish 5 (9718) Detections
```{r}

f5_freq <- f5_9718 %>%
  mutate(freq= 1) %>%
  group_by(station, lat, long) %>%
  summarise(freq=sum(freq))

#converting to spatial
data(f5_freq, package = "sp")
f5_freq_sf <- st_as_sf(f5_freq, coords= c("long","lat"), crs=4326)
f5_freq_sp <- as(f5_freq_sf, "Spatial")

f5_freq_map <- ggplot(data = statGPS_sf) +
  geom_sf(color= "gray76")+
 geom_sf(data= f5_freq_sf, aes(color = f5_freq_sf$freq))+
  scale_colour_viridis_c() +
  geom_sf(data = ca, color = "darkgreen", fill = "darkgreen") +
  ggtitle("Detections f5(9718)")+
  coord_sf(xlim = c(-119.01, -119.06), ylim = c(33.46, 33.495))+
  theme_bw()

f5_freq_map

```


##4. Diurnal Movement Patterns

For these plots the time stamp is seperated out by day (x axis) and hour of the day (y axis) to see if there is a pattern in movement asosciated with the time of the day.


**Fish 1: 9718**
```{r}

f1di <- f1_29792 %>%
  separate(date_time, c("date", "time"), sep = " ")%>%
  separate(time, c("hour", "minute", "second"), sep = ":") %>%
  dplyr::select(date, hour, transmitter, station, long, lat)

#converting to POSIX is not working for some reason, this may be important in the future but perphaps not
#as.POSIXct(f5di$date, format="%Y-%m-%d")
#as.POSIXct(f5di$time, format="%h-%m-%s")


#1 fish
f1di_graph <-ggplot(f1di, aes(x=date, y= hour )) +
       geom_point(shape=15) +
       theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ggtitle("Transmitter #29792") 
    
#    scale_y_continuous(breaks=c(00:00:00,08:00:00, 16:00:00, 24:00:00))

f1di_graph

```

**Fish 2: 9712**
```{r}

f2di <- f2_9712 %>%
  separate(date_time, c("date", "time"), sep = " ")%>%
  separate(time, c("hour", "minute", "second"), sep = ":") %>%
  dplyr::select(date, hour, transmitter, station, long, lat)

#converting to POSIX is not working for some reason, this may be important in the future but perphaps not
#as.POSIXct(f5di$date, format="%Y-%m-%d")
#as.POSIXct(f5di$time, format="%h-%m-%s")


#1 fish
f2di_graph <-ggplot(f2di, aes(x=date, y= hour )) +
       geom_point(shape=15) +
       theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ggtitle("Transmitter #29792") 
#    scale_y_continuous(breaks=c(00:00:00,08:00:00, 16:00:00, 24:00:00))

f2di_graph

```


**Fish 3: 9714**
```{r}

f3di <- f3_9714 %>%
  separate(date_time, c("date", "time"), sep = " ")%>%
  separate(time, c("hour", "minute", "second"), sep = ":") %>%
  dplyr::select(date, hour, transmitter, station, long, lat)

#converting to POSIX is not working for some reason, this may be important in the future but perphaps not
#as.POSIXct(f5di$date, format="%Y-%m-%d")
#as.POSIXct(f5di$time, format="%h-%m-%s")


#1 fish
f3di_graph <-ggplot(f3di, aes(x=date, y= hour )) +
       geom_point(shape=15) +
       theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ggtitle("Transmitter #9714") 
#    scale_y_continuous(breaks=c(00:00:00,08:00:00, 16:00:00, 24:00:00))

f3di_graph

```


**Fish 4: 9716**
```{r}

f4di <- f4_9716 %>%
  separate(date_time, c("date", "time"), sep = " ") %>%
  separate(time, c("hour", "minute", "second"), sep = ":") %>%
  dplyr::select(date, hour, transmitter, station, long, lat)

#converting to POSIX is not working for some reason, this may be important in the future but perphaps not
#as.POSIXct(f5di$date, format="%Y-%m-%d")
#as.POSIXct(f5di$time, format="%h-%m-%s")


#1 fish
f4di_graph <-ggplot(f4di, aes(x=date, y= hour )) +
       geom_point(shape=15) +
       theme(axis.text.x = element_text(angle = 90, hjust = 1)) +       
       ggtitle("Transmitter #9716") 
#    scale_y_continuous(breaks=c(00:00:00,08:00:00, 16:00:00, 24:00:00))

f4di_graph

```



**Fish 5: 9718**
```{r}

f5di <- f5_9718 %>%
  separate(date_time, c("date", "time"), sep = " ")%>%
  separate(time, c("hour", "minute", "second"), sep = ":") %>%
  dplyr::select(date, hour, transmitter, station, long, lat)

#converting to POSIX is not working for some reason, this may be important in the future but perphaps not
#as.POSIXct(f5di$date, format="%Y-%m-%d")
#as.POSIXct(f5di$time, format="%H-%M-%S")


#5 fish
f5di_graph <-ggplot(f5di, aes(x=date, y= hour )) +
       geom_point(shape=15) +
       theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ggtitle("Transmitter #9718") 

f5di_graph

```

##5. Seasonal Variations
*When enough data comes through*
bar graph; x= calender month, y= number of detections per month



```{r}

all_monthly <- detec %>%
  mutate(freq= 1) %>%
  separate(date_time, c("date", "time"), sep= " ") %>%
  separate(date, c("year", "month", "day"), sep = "-") %>%
  group_by(year, month) %>%
  summarise(detections=sum(freq))


 monthly_bar <- ggplot(data=all_monthly, aes(x=month, y=detections, fill= year)) +
   geom_bar(stat="identity" )+
  theme_bw()+
  ggtitle("Total detections by month")
monthly_bar


```








