---
title: "notebook: using og data given"
author: "Juliette Verstaen"
date: "4/9/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load packages
```{r}
library(tidyverse)
library(sf)
library(sp)
library(ggpubr)
library(readxl)
library(lubridate)
library(adehabitatLT)
library(raster)
library(rworldmap)

```

Data Loading
```{r}

detec <- read_csv("data/GSBdetections_SBI_4_3_19offload.csv")

#rename columns
names(detec) <- c("date_time", "receiver", "transmitter", "station", "lat", "long", "notes")

```

4/10/19: TO DO
- left off in the data wrangling section messing with detec to make station numbers 01 instead of 1 so that the abaus thing works. 
- need to graph the rest of the fish, should be straightforward sicne I alreayd did it for one
- don't need to seperate out each station, go back through and make sure if not not then delete it

Data Wrangling

```{r}

#pick and simplify the data that we need
detec <- detec %>%
  select("date_time", "transmitter", "station", "lat", "long") %>%
  separate(transmitter, c("first", "second", "transmitter")) %>%
  select("date_time", "transmitter", "station", "long", "lat") 

#detec <- gsub("SB-1","SB-01", detect )
detec$station[detec$station == "SB-1"] <- "SB-01"
detec$station[detec$station == "SB-2"] <- "SB-02"
detec$station[detec$station == "SB-3"] <- "SB-03"
detec$station[detec$station == "SB-4"] <- "SB-04"
detec$station[detec$station == "SB-5"] <- "SB-05"
detec$station[detec$station == "SB-6"] <- "SB-06"
detec$station[detec$station == "SB-7"] <- "SB-07"
detec$station[detec$station == "SB-8"] <- "SB-08"
detec$station[detec$station == "SB-9"] <- "SB-09"


#convert the lat/longs to actual spatial points/classes
detec_sf <- st_as_sf(detec, coords= c("long","lat"), crs=4326)
detec_sp <- as(detec_sf, "Spatial")

```

Changing the time to standard convention
##this was part of my OG raw data wrangling for data time class
```{r}

library(lubridate)

#making the time correct
detec <- detec %>%
  separate(date_time, c("date", "time"), sep= " ")%>%
  separate(time, c("minute", "second", sep= ":")) 

##Date stuff is weird so trying to fix that
# minutes need to ahve 2 digits
minutes_2digits <-  sprintf("%02s", detec$minute)
#order of the date is wrong
reorder_date <- as.Date(parse_date_time(detec$date,"mdy"))

#need to bind them back together with the main df since they are vectors
detec_new_1 <- cbind(detec, reorder_date)
detec_new <- cbind(detec_new_1, minutes_2digits)

detec_spatial <- detec_new %>%
  unite(time, minutes_2digits, second, sep = ":") %>%
  unite(date_time, reorder_date, time, sep = " ")%>%
  select("date_time", "transmitter", "station", "lat", "long")

detec_time <- detec_new %>%
  unite(time, minutes_2digits, second, sep = ":") %>%
  unite(date_time, reorder_date, time, sep = "T")%>%
  select("date_time", "transmitter", "station", "lat", "long")

#change the class so that R recognizes it as date and time aka POSIXct
detec_time$date_time <- as.POSIXct(detec_time$date_time, format="%Y-%m-%dT%H:%M")
#head(detec_posix)

#check that the date time is in the proper class
class(detec_time$date_time)

#convert the lat/longs to actual spatial points/classes
detec_sf <- st_as_sf(detec_spatial, coords= c("long","lat"), crs=4326)
detec_sp <- as(detec_sf, "Spatial")


```


Abacus Graphs
seperate by fish and station
```{r}

# 1 fish
all_29792 <- detec_time %>%
  filter(transmitter == "29792")

#2 fish
all_9712 <- detec_time %>%
  filter(transmitter == "9712")

#3 fish
all_9714 <- detec_time %>%
  filter(transmitter == "9714")

#4 fish
all_9716 <- detec_time %>%
  filter(transmitter == "9716")

#5 fish
all_9718 <- detec_time %>%
  filter(transmitter == "9718")

```

##Ploting Abaus graphs 
1 fish
```{r}

all_29792
class(all_29792$date_time)

#1 fish
f1 <-ggplot(all_29792, aes(x=date_time, y= station )) +
       geom_point() +
       theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
       scale_x_datetime() +
  ggtitle("Reciever #29792")

f1


```

2 fish
```{r}

#2 fish
f2 <-ggplot(all_9712, aes(x=date_time, y= station )) +
       geom_point() +
       theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
       scale_x_datetime() +
  ggtitle("Reciever #9712")

f2


```

3 fish
```{r}

#3 fish
f3 <-ggplot(all_9714, aes(x=date_time, y= station )) +
       geom_point() +
       theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
       scale_x_datetime() +
  ggtitle("Reciever #9714")

f3

```

4 fish
```{r}

#4 fish
f4 <-ggplot(all_9716, aes(x=date_time, y= station )) +
       geom_point() +
       theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
       scale_x_datetime() +
  ggtitle("Reciever #9716")

f4

```

5 fish
```{r}

#5 fish
f5 <-ggplot(all_9718, aes(x=date_time, y= station )) +
       geom_point() +
       theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
       scale_x_datetime() +
  ggtitle("Reciever #9718")

f5

```

All Abacus Graphs on One

```{r}

all_abacus <- ggarrange(f1, f2, f3,f4, f5 , 
          ncol = 2, nrow = 3)

#f3 only has one obsrvation

all_abacus
ggsave("all_abacus.jpg", width=5, height=7, dpi=300)

```

Mapping Detections/Hr for 29792
Frequency detections per hour
http://www.r-gators.com/2018/01/31/wildlife-tracking-data-in-r/
##THIS IS CREATING TRAJECTORY CLASS WITH DATA
```{r}

class(all_29792)

#calling this test for now to make it easier. using all_29792; make it back to that after figure it out
test <- all_29792 

class(test)

data(test, package = "sp")
test_sf <- st_as_sf(test, coords= c("long","lat"), crs=4326)
test_sp <- as(test_sf, "Spatial")

class(test_sp$date_time)

#creating ltraj object

raw_test <- as.ltraj(coordinates(test_sp),date=test_sp$date_time,id=test_sp$transmitter, typeII=TRUE)

is.regular(raw_test)

```

###was doing this for mapping detection
Data wrangling for: 29792
```{r}

all_29792 <- detec %>%
  filter(transmitter == "29792")

freq_29792 <- all_29792 %>%
   separate(date_time, c("date", "time"), sep= " ")%>%
   separate(time, c("hour", "minute", "second"), sep= ":") %>%
 # mutate(occur = 1) %>%
  group_by(date, hour, station)%>%
 # summarize(freq=sum(occur)) %>%
   mutate(lat = station) %>%
  mutate(long = station) %>%
  select(date, station,  long, lat)

#adding coordinates
# Station 1
freq_29792$lat <- replace(freq_29792$lat, freq_29792$lat == "SB-01", "33.48818")
freq_29792$long <- replace(freq_29792$long, freq_29792$long == "SB-01", "- 119.0249")

# Station 2
freq_29792$lat <- replace(freq_29792$lat, freq_29792$lat == "SB-02", "33.49063")
freq_29792$long <- replace(freq_29792$long, freq_29792$long == "SB-02", "- 119.0317")

# Station 3
freq_29792$lat <- replace(freq_29792$lat, freq_29792$lat == "SB-03", "33.48695")
freq_29792$long <- replace(freq_29792$long, freq_29792$long == "SB-03", "- 119.0405")

# Station 5
freq_29792$lat <- replace(freq_29792$lat, freq_29792$lat == "SB-05", "33.47595")
freq_29792$long <- replace(freq_29792$long, freq_29792$long == "SB-05", "- 119.0476")

# Station 6
freq_29792$lat <- replace(freq_29792$lat, freq_29792$lat == "SB-06", "33.46800")
freq_29792$long <- replace(freq_29792$long, freq_29792$long == "SB-06", "- 119.0457")

# Station 7
freq_29792$lat <- replace(freq_29792$lat, freq_29792$lat == "SB-07", "33.46367")
freq_29792$long <- replace(freq_29792$long, freq_29792$long == "SB-07", "- 119.0418")

# Station 8
freq_29792$lat <- replace(freq_29792$lat, freq_29792$lat == "SB-08", "33.46065")
freq_29792$long <- replace(freq_29792$long, freq_29792$long == "SB-08", "- 119.0348")

# Station 9
freq_29792$lat <- replace(freq_29792$lat, freq_29792$lat == "SB-09", "33.47087")
freq_29792$long <- replace(freq_29792$long, freq_29792$long == "SB-09", "- 119.0260")

# Station 10
freq_29792$lat <- replace(freq_29792$lat, freq_29792$lat == "SB-10", "33.48382")
freq_29792$long <- replace(freq_29792$long, freq_29792$long == "SB-10", "- 119.0228")




```


##############

Plotting Dectections
```{r}

#download coastline shapefile
library(rnaturalearth)
library(rgeos)
#download coast shapefile (?)
coast <- rnaturalearth::ne_countries(scale = "large",
                                     country = "United States of America",
                                     returnclass = "sf")

#plot all; can't see a lot of them beause on top of each other
sbi_detec <- ggplot(data = detec_sf) +
  geom_sf(aes(color = detec_sf$transmitter))+
  geom_sf(data = coast, color = "darkgreen", fill = "darkgreen") +
  ggtitle("Giant Seabass Dections August- Septemeber 2018")+
  ggtitle("Giant Seabass Dections August- Septemeber 2018")+
  coord_sf(xlim = c(-119.01, -119.06), ylim = c(33.46, 33.495))
  
sbi_detec

#plot 29792

detec_29792<- detec_sf %>%
  filter(transmitter == "29792")%>%
  select("date_time", "transmitter", "geometry")

detec_29792_plot <- ggplot(data = detec_29792) +
  geom_sf(aes(color = detec_29792$date_time))+
  geom_sf(data = coast, color = "darkgreen", fill = "darkgreen") +
  ggtitle("Giant Seabass Dections August- Septemeber 2018")+
  ggtitle("Giant Seabass Dections August- Septemeber 2018")+
  coord_sf(xlim = c(-119.01, -119.06), ylim = c(33.46, 33.495))+
  #scale_color_continuous()+
  theme(axis.text.x=element_text(angle=90, hjust=1)) 
  
detec_29792_plot

```

Past Work:


Changing the date/time to be recognizable by R
- turns out that sf package can't read this type of class data so it won't work
```{r}

#library(lubridate)

#pick and simplify the data that we need
#detec <- detec %>%
#  select("date_time", "transmitter", "station", "lat", "long") %>%
#  separate(transmitter, c("first", "second", "transmitter")) %>%
#  select("date_time", "transmitter", "station", "long", "lat") %>%
#  separate(date_time, c("date", "time"), sep= " ")%>%
#  separate(time, c("minute", "second", sep= ":")) 

##Date stuff is weird so trying to fix that
# minutes need to ahve 2 digits
#minutes_2digits <-  sprintf("%02s", detec$minute)
# order of the date is wrong
#reorder_date <- as.Date(parse_date_time(detec$date,"mdy"))

#need to bind them back together with the main df since they are vectors
#detec_new_1 <- cbind(detecTEST, reorder_date)
#detec_new <- cbind(detec_new_1, minutes_2digits)

#detec_new <- detec_new %>%
#  unite(time, minutes_2digits, second, sep = ":") %>%
#  unite(date_time, reorder_date, time, sep = "T")%>%
#  select("date_time", "transmitter", "station", "lat", "long")

#change the class so that R recognizes it as date and time aka POSIXct
#detec_posix <- as.POSIXct(detec_new$date_time, format="%Y-%m-%dT%H:%M")
#head(detec_posix)

#check that the date time is in the proper class
#class(detec_new$date_time)


```



####Mapping Movement Trajectory by the hour
###4/16/19

##trying to use HabitatLR package: I don't think this is possible because of the irregular trajectory. this means that the "descriptive parameters of these trajectories may not becompared when computed on different time lags"
```{r}

##this detec is from this file : detec <- read_csv("data/Detections_Juliette.csv")
# run the first chunk from the final Rmarkdown file

f1_29792 <- detec %>%
  filter(transmitter == "29792")

#calling this test for now to make it easier. using all_29792; make it back to that after figure it out
test <- f1_29792 %>%
#  mutate(x = "NA") %>%
#  mutate(y = "NA")
  
#  mutate(freq= 1)

#####Figure out how to group or bin or cut by hour and then sum 

#this?
#test$total_freq <- cut(test$date_time, breaks="hour")
#aggregate(test$freq,by=list(test$hour),FUN=sum)

#or this?
#test_hourdetec <- do.call('data.frame', aggregate(freq~
              #   cbind(Hour=format(date_time,'%HH')), test, sum))
#test_hourdetec$Hour
#Hour 
# 16 
#Levels: 16


#res$Hour <- as.numeric(as.character(res$Hour))
#with(res, plot(Hour, Speed))

#following more exactly along with the example
#test <- test[!is.na(test$x),]
#test <- test[!is.na(test$y),]

#coordinates(test) <- c("long", "lat")

#proj4string(test) <- CRS("+init=epsg:32617")
#class(test)

#this was the way i normall do it
#converting to spatial coordinates
data(test, package = "sp")
test_sf <- st_as_sf(test, coords= c("long","lat"), crs=4326)
test_sp <- as(test_sf, "Spatial")

class(test_sp$date_time)
#check to make sure its class: "POSIXct" "POSIXt" 

#creating ltraj object
raw_test <- as.ltraj(coordinates(test_sp),date=test_sp$date_time,id=test_sp$transmitter, typeII=TRUE)

#test if the trajectory is regular (ie. constant time lag between successive relocations)
#should be FALSE because of the type of tracking equipement used
is.regular(raw_test)

raw_test
#only 1 burst because we have filtered out only one tracker (each burst has a bunch of info within)

head(raw_test[[1]])

plot(raw_test)


```
###################################################
#### 4/17/19
###################################################
# 
```{r}

##this detec is from this file : detec <- read_csv("data/Detections_Juliette.csv")
# run the first chunk from the final Rmarkdown file
f1_29792 <- detec %>%
  filter(transmitter == "29792")

#calling this test for now to make it easier. using all_29792; make it back to that after figure it out
#the grouping i did should have worked but double check R logit behind it

##data wrangle
test <- f1_29792 %>%
  mutate(freq= 1) %>%
  separate(date_time, c("date", "time"), sep= " ") %>%
  separate(time, c("hour", "minute", "second"), sep = ":") %>%
  group_by(date, hour, transmitter, station, lat, long) %>%
  summarise(freq=sum(freq)) %>%
  mutate(minute= "00") %>%
  mutate(second= "00") %>%
  unite(time_1, minute, second, sep= ":")%>%
  unite(time, hour, time_1, sep = ":") %>%
  unite(date_time, date, time, sep = " ")

#changing classes for time and coordinates
test$date_time <- as.POSIXct(test$date_time, format="%Y-%m-%d %H:%M")
data(test, package = "sp")
test_sf <- st_as_sf(test, coords= c("long","lat"), crs=4326)
test_sp <- as(test_sf, "Spatial")

#map dectections by frequency= color

testmap <- ggplot(data = test_sf) +
  geom_sf(aes(color = test_sf$freq))+
  #geom_sf(data = coast, color = "darkgreen", fill = "darkgreen") +
  ggtitle("Giant Seabass Dections August- Septemeber 2018")+
  coord_sf(xlim = c(-119.01, -119.06), ylim = c(33.46, 33.495))

testmap


```

#### great lakes acoustic package

```{r}
##install
install.packages("remotes")
library(remotes) 
install_url("https://gitlab.oceantrack.org/GreatLakes/glatos/repository/master/archive.zip",
              build_opts = c("--no-resave-data", "--no-manual"))  
library(glatos)

test <- detec %>%
  filter(transmitter == "29792")

names(test) <- c("detection_timestamp_utc", "transmitter", "station", "long", "lat")

#class(test$date_time)
         
data(test, package = "sp")
test_sf <- st_as_sf(test, coords= c("long","lat"), crs=4326)
test_sp <- as(test_sf, "Spatial")

st_geometry(test_sf) <- "location_col"
  

test_ab <- abacus_plot(test_sf[
test_sf$transmitter == 29792,], location_col='glatos_array', detection_timestamp_utc ='glatos_array', main='Fish 1: 29792')


```

##attempts at mapping detections
#the grouping i did should have worked but double check R logit behind it

Fish 1: 29792
```{r}

##data wrangle

f1_hourly <- detec %>%
  filter(transmitter == "29792")%>%
  mutate(freq= 1) %>%
  separate(date_time, c("date", "time"), sep= " ") %>%
  separate(time, c("hour", "minute", "second"), sep = ":") %>%
  group_by(date, hour, transmitter, station, lat, long) %>%
  summarise(freq=sum(freq)) %>%
  mutate(minute= "00") %>%
  mutate(second= "00") %>%
  unite(time_1, minute, second, sep= ":")%>%
  unite(time, hour, time_1, sep = ":") %>%
  unite(date_time, date, time, sep = " ")

#changing classes for time and coordinates
f1_hourly$date_time <- as.POSIXct(f1_hourly$date_time, format="%Y-%m-%d %H:%M")
data(f1_hourly, package = "sp")
f1_hourly_sf <- st_as_sf(f1_hourly, coords= c("long","lat"), crs=4326)
f1_hourly_sp <- as(f1_hourly_sf, "Spatial")

#map dectections by frequency= color

f1_hourly_map <- ggplot(data = f1_hourly_sf) +
  geom_sf(aes(color = f1_hourly_sf$freq))+
  geom_sf(data = ca, color = "darkgreen", fill = "darkgreen") +
  ggtitle("29792 Frequency August- Septemeber 2018")+
  coord_sf(xlim = c(-119.01, -119.06), ylim = c(33.46, 33.495))

f1_hourly_map


```


Fish 2: 9712
```{r}

##data wrangle

f2_hourly <- detec %>%
  filter(transmitter == "9712")%>%
  mutate(freq= 1) %>%
  separate(date_time, c("date", "time"), sep= " ") %>%
  separate(time, c("hour", "minute", "second"), sep = ":") %>%
  group_by(date, hour, transmitter, station, lat, long) %>%
  summarise(freq=sum(freq)) %>%
  mutate(minute= "00") %>%
  mutate(second= "00") %>%
  unite(time_1, minute, second, sep= ":")%>%
  unite(time, hour, time_1, sep = ":") %>%
  unite(date_time, date, time, sep = " ")

#changing classes for time and coordinates
f2_hourly$date_time <- as.POSIXct(f2_hourly$date_time, format="%Y-%m-%d %H:%M")
data(f2_hourly, package = "sp")
f2_hourly_sf <- st_as_sf(f2_hourly, coords= c("long","lat"), crs=4326)
f2_hourly_sp <- as(f2_hourly_sf, "Spatial")

#map dectections by frequency= color

f2_hourly_map <- ggplot(data = f2_hourly_sf) +
  geom_sf(aes(color = f2_hourly_sf$freq))+
  geom_sf(data = ca, color = "darkgreen", fill = "darkgreen") +
  ggtitle("9712 Frequency August- Septemeber 2018")+
  coord_sf(xlim = c(-119.01, -119.06), ylim = c(33.46, 33.495))

f2_hourly_map


```


Fish 3: 9714
```{r}

##data wrangle

f3_hourly <- detec %>%
  filter(transmitter == "9714")%>%
  mutate(freq= 1) %>%
  separate(date_time, c("date", "time"), sep= " ") %>%
  separate(time, c("hour", "minute", "second"), sep = ":") %>%
  group_by(date, hour, transmitter, station, lat, long) %>%
  summarise(freq=sum(freq)) %>%
  mutate(minute= "00") %>%
  mutate(second= "00") %>%
  unite(time_1, minute, second, sep= ":")%>%
  unite(time, hour, time_1, sep = ":") %>%
  unite(date_time, date, time, sep = " ")

#changing classes for time and coordinates
f3_hourly$date_time <- as.POSIXct(f3_hourly$date_time, format="%Y-%m-%d %H:%M")
data(f3_hourly, package = "sp")
f3_hourly_sf <- st_as_sf(f3_hourly, coords= c("long","lat"), crs=4326)
f3_hourly_sp <- as(f3_hourly_sf, "Spatial")

#map dectections by frequency= color

f3_hourly_map <- ggplot(data = f3_hourly_sf) +
  geom_sf(aes(color = f3_hourly_sf$freq))+
  geom_sf(data = ca, color = "darkgreen", fill = "darkgreen") +
  ggtitle("9714 Frequency August- Septemeber 2018")+
  coord_sf(xlim = c(-119.01, -119.06), ylim = c(33.46, 33.495))

f3_hourly_map


```


Fish 4: 9716
```{r}

##data wrangle

f4_hourly <- detec %>%
  filter(transmitter == "9716")%>%
  mutate(freq= 1) %>%
  separate(date_time, c("date", "time"), sep= " ") %>%
  separate(time, c("hour", "minute", "second"), sep = ":") %>%
  group_by(date, hour, transmitter, station, lat, long) %>%
  summarise(freq=sum(freq)) %>%
  mutate(minute= "00") %>%
  mutate(second= "00") %>%
  unite(time_1, minute, second, sep= ":")%>%
  unite(time, hour, time_1, sep = ":") %>%
  unite(date_time, date, time, sep = " ")

#changing classes for time and coordinates
f4_hourly$date_time <- as.POSIXct(f4_hourly$date_time, format="%Y-%m-%d %H:%M")
data(f4_hourly, package = "sp")
f4_hourly_sf <- st_as_sf(f4_hourly, coords= c("long","lat"), crs=4326)
f4_hourly_sp <- as(f4_hourly_sf, "Spatial")

#map dectections by frequency= color

f4_hourly_map <- ggplot(data = f4_hourly_sf) +
  geom_sf(aes(color = f4_hourly_sf$freq))+
  geom_sf(data = ca, color = "darkgreen", fill = "darkgreen") +
  ggtitle("9716 Frequency August- Septemeber 2018")+
  coord_sf(xlim = c(-119.01, -119.06), ylim = c(33.46, 33.495))

f4_hourly_map


```


Fish 5: 9718
```{r}

##data wrangle

f5_hourly <- detec %>%
  filter(transmitter == "9718")%>%
  mutate(freq= 1) %>%
  separate(date_time, c("date", "time"), sep= " ") %>%
  separate(time, c("hour", "minute", "second"), sep = ":") %>%
  group_by(date, hour, transmitter, station, lat, long) %>%
  summarise(freq=sum(freq)) %>%
  mutate(minute= "00") %>%
  mutate(second= "00") %>%
  unite(time_1, minute, second, sep= ":")%>%
  unite(time, hour, time_1, sep = ":") %>%
  unite(date_time, date, time, sep = " ")

#changing classes for time and coordinates
f5_hourly$date_time <- as.POSIXct(f5_hourly$date_time, format="%Y-%m-%d %H:%M")
data(f5_hourly, package = "sp")
f5_hourly_sf <- st_as_sf(f5_hourly, coords= c("long","lat"), crs=4326)
f5_hourly_sp <- as(f5_hourly_sf, "Spatial")

#map dectections by frequency= color

f5_hourly_map <- ggplot(data = f5_hourly_sf) +
  geom_sf(aes(color = f5_hourly_sf$freq))+
  geom_sf(data = ca, color = "darkgreen", fill = "darkgreen") +
  ggtitle("9718 Frequency August- Septemeber 2018")+
  scale_colour_viridis_c() +
  coord_sf(xlim = c(-119.01, -119.06), ylim = c(33.46, 33.495))

f5_hourly_map


```


All Fish
```{r}

##data wrangle

all_hourly <- detec %>%
  mutate(freq= 1) %>%
  separate(date_time, c("date", "time"), sep= " ") %>%
  separate(time, c("hour", "minute", "second"), sep = ":") %>%
  group_by(transmitter, date, hour, transmitter, station, lat, long) %>%
  summarise(freq=sum(freq)) %>%
  mutate(minute= "00") %>%
  mutate(second= "00") %>%
  unite(time_1, minute, second, sep= ":")%>%
  unite(time, hour, time_1, sep = ":") %>%
  unite(date_time, date, time, sep = " ")

#changing classes for time and coordinates
all_hourly$date_time <- as.POSIXct(all_hourly$date_time, format="%Y-%m-%d %H:%M")
data(all_hourly, package = "sp")
all_hourly_sf <- st_as_sf(all_hourly, coords= c("long","lat"), crs=4326)
all_hourly_sp <- as(all_hourly_sf, "Spatial")

#map dectections by frequency= color

all_hourly_map <- ggplot(data = all_hourly_sf) +
  geom_sf(aes(color = all_hourly_sf$freq))+
  scale_colour_viridis_c() +
  geom_sf(data = ca, color = "darkgreen", fill = "darkgreen") +
  ggtitle("All Frequency August- Septemeber 2018")+
  coord_sf(xlim = c(-119.01, -119.06), ylim = c(33.46, 33.495))

all_hourly_map


```


4/22/2019
#### Trying to see if can use trajectory class in stuff from the HR package

```{r}

f1_29792 <- detec %>%
  filter(transmitter == "29792")

#test makes it easier for naming stuff when working through it
test <- f1_29792 

#converting to spatial coordinates
data(test, package = "sp")
test_sf <- st_as_sf(test, coords= c("long","lat"), crs=4326)
test_sp <- as(test_sf, "Spatial")

class(test_sp$date_time)
#check to make sure its class: "POSIXct" "POSIXt" 

#creating ltraj object
raw_test <- as.ltraj(coordinates(test_sp),date=test_sp$date_time,id=test_sp$transmitter, typeII=TRUE)


```


trying to figure out how to edit the time on y axis so not a giant mess
```{r}

time_vector <- c("00:00:00", "06:00:00", "12:00:00", "18:00:00", "24:00:00")
as.POSIXct(time_vector, format="%X")


test <- seq(ISOtime(200,1,31), by = "month", length.out = 4)

start_time = strptime("00:00:00", format = "%H:%M:%S")
end_time = strptime("23:59:59", format = "%H:%M:%S")
breaks = seq(0, 125, length.out = 4)
labels = c("00:00:00", "06:00:00", "12:00:00", 
           "18:00:00")

```


binning by the hour code for abacud graphs: wasn't super interesting but at lease i have the code now
Binned by hour

```{r}

hourly_4 <- detec %>% 
  filter(transmitter == "9716") %>%
  mutate(freq= 1) %>%
  separate(date_time, c("date", "time"), sep= " ") %>%
  separate(time, c("hour", "minute", "second"), sep = ":") %>%
  group_by(transmitter, date, hour, transmitter, station, lat, long) %>%
  summarise(freq=sum(freq)) %>%
  mutate(minute= "00") %>%
  mutate(second= "00") %>%
  unite(time_1, minute, second, sep= ":")%>%
  unite(time, hour, time_1, sep = ":") %>%
  unite(date_time, date, time, sep = " ")
#changing classes for time and coordinates
hourly_4$date_time <- as.POSIXct(hourly_4$date_time, format="%Y-%m-%d %H:%M")

f4_hourly <-ggplot(hourly_4, aes(x=date_time, y= station)) +
       geom_point(shape=15) +
       theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ggtitle("Transmitter #9716") +
   scale_x_datetime()
  
f4_hourly


```



