---
title: "Squid Satellite Proof of Concept"
author: "Juliette Verstaen"
date: "5/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}

library(tidyverse)
library(ncdf4)
library(ncdf.tools)
library(rerddap)
library(akima)
library(dplyr)
library(ggplot2)
library(mapdata)
library(ncdf4)
library(plot3D)

```


###kml files
Found some data that I thought could be what we wanted in kml format. Did not work

```{r}

library(sf)
library(gdalUtils)

test <- st_read("data/collections.kml")

testmap <- ggplot(data = test) +
  geom_sf()

ogrInfo("collections.kml",layer="collections")
polysFromKML=readOGR("collections.kml",layer="collections") 
class(polysFromKML)
plot(polysFromKML) 

```

file_naming_convention = VNP02DNB.AYYYYDDD.HHMM.CCC.YYYYDDDHHMMSS.nc AYYYYDDD = Acquisition Year and Day of Year HHMM = Acquisition Hour and Minute CCC = Collection number YYYYDDDHHMMSS = Production Date and Time nc = NetCDF4

###Getting data from netCDF file
```{r}

### load the ncdf4 package
library(ncdf4)

### set the path and filename
ncpath <- "data/ncfiles/"
ncname <- "test"  
ncfname <- paste(ncpath, ncname, ".nc4", sep="")
dname <- "BinScheme1_ScienceData_Radiance"

### open the netCDF file
ncin <- nc_open(ncfname)
print(ncin)

### name of all the varibables in this file
names(ncin$var)

### get lattitude and longitude
lat <- ncvar_get(ncin,"BinScheme1_GeolocationData_Latitude")
nlat <- dim(lat)
head(lat)

lon <- ncvar_get(ncin,"BinScheme1_GeolocationData_Longitude")
nlon <- dim(lon)
head(lon)

### get the radiance 
rad <- ncvar_get(ncin, "BinScheme1_ScienceData_Radiance")
rad

### get the units for the radiance (this seems like its very important/helpful when using time units ie: units are different for each piece of information)
rad_units <- ncatt_get(ncin, "BinScheme1_ScienceData_Radiance", "units")
nt <- dim(rad)
nt

rad_units
### hasatt means that rad-units has two components: hasatt = logical variable, and value = the actual units

### get radiance
rad_array <- ncvar_get(ncin,dname)
dlname <- ncatt_get(ncin,dname,"long_name")
dunits <- ncatt_get(ncin,dname,"units")
fillvalue <- ncatt_get(ncin,dname,"_FillValue")
dim(rad_array)

### get global attributes
title <- ncatt_get(ncin,0,"title")
institution <- ncatt_get(ncin,0,"institution")
datasource <- ncatt_get(ncin,0,"source")
references <- ncatt_get(ncin,0,"references")
history <- ncatt_get(ncin,0,"history")
Conventions <- ncatt_get(ncin,0,"Conventions")
time_start <- ncatt_get(ncin,0,"time_coverage_start")
time_end <- ncatt_get(ncin,0,"time_coverage_end")

### this is not necessary in the code but useful information for knowing the names of the varibles in your file
# name of all the varibables in this file
names(ncin$var)

### close the netCDF file
nc_close(ncin)

### check to make sure the objects you extracted above are in your workshape
ls()

```


###Reshaping from raster to rectangle
Attempts to visulize the radiance data on a map
```{r}

### load some packages
library(chron)
library(lattice)
library(RColorBrewer)

### replace netCDF fill values with NA's
rad_array[rad_array==fillvalue$value] <- NA

length(na.omit(as.vector(rad_array[,,1])))

m <- 1
rad_slice <- rad_array[,,m]

image(lon,lat,rad_slice)

col=rev(brewer.pal(10,"RdBu"))

```









