---
title: "ADEHabitatHR Package walk through"
author: "Juliette Verstaen"
date: "4/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**ADEHabitatHR Package**

```{r}

library(adehabitatHR)
library(sp)
library(maptools)

# adehabitatHR provides  classes  and  methods  for  dealing  with home range analysis

# adehabitatHS provides classes and methods for dealing with habitat selection 

# adehabitatLT provides classes and methods for dealing with animals trajectory

# adehabitatMA provides classes and methods for dealing with maps

```

1. Example dataset
```{r}
data(puechabonsp)
names(puechabonsp)

head(as.data.frame(puechabonsp$relocs))

## Map of the elevation
image(puechabonsp$map, col=grey(c(1:10)/10))
## map of the relocations
plot(puechabonsp$relocs, add=TRUE,
  col=as.data.frame(puechabonsp$relocs)[,1])

```

2. The Minimum Convex Polygon (MCP)


```{r}

# Remove the 5% of extreme points. The idea is that animals will make further journeys every once and a while which is outside of their normal range.
data(puechabonsp)
cp <- mcp(puechabonsp$relocs[,1], percent=95)
#The results are stored in an object of class SpatialPolygonsDataFrame
class(cp)

#can use sp and maptools functions to plot your spatial data
plot(cp)
plot(puechabonsp$relocs, add=TRUE)

#convert to a shapefile that can be read into GIS
library(maptools)
writePolyShape(cp, "homerange")


```

3.1 Overlay operations
```{r}
head(as.data.frame(puechabonsp$map))

#We may identify the pixels of this map enclosed in each home range using the function over from the package sp
#1= pixel is in home range; NA= pixel not in homerange
enc <- over(puechabonsp$map, cp[,2], fn=function(x) return(1))
head(enc)

#transform into vector
coordinates(enc) <- coordinates(puechabonsp$map)
gridded(enc) <- TRUE
#The result is shown below, in black, on an elevation map:
image(puechabonsp$map)
image(enc, add=TRUE, col="black", useRasterImage=FALSE)

#However, because the rasterization of home ranges is a common operation, I included a function hr.rast to make this operation more straightforward:
cprast <- hr.rast(cp, puechabonsp$map)
#resulting object is a SpatialPixelsDataFrame with one column per animal
par(mar=c(0,0,0,0))
par(mfrow=c(2,2)) 
  for (i in 1:4) {
  image(cprast[,i], useRasterImage=FALSE)
  box()
    }
```

3.2.Computation of home-range sizes
Home-range size is automatically computed by the mcr function
```{r}
as.data.frame(cp)
#default area is in hectares

# we excluded the top 5% extreme relocations. below shows you all
hrs <- mcp.area(puechabonsp$relocs[,1], percent=seq(50, 100, by = 5))
# except for calou this exlcusion seems to make sense

#Note that the results of the function mcp.area are stored in a data frame of class "hrsize" and can be used for further analysis:
hrs

```

4.1 The kernel estimation and the utlization distribution
- utilization distribution (UD, van Winkle, 1975): animals use of space can be described by a bivariate probability density function
- deciding how much the smoothing parameter should be (h) is important/makes a big difference

4.2 The function kernelUD: estimating the utilization distribution
```{r}

data(puechabonsp)
kud <- kernelUD(puechabonsp$relocs[,1], h="href")
# if h = "href", the “reference” bandwidth is used in the estimation
# if h = "LSCV", the “LSCV” bandwidth is used in the estimation
kud
image(kud)

#The values of the smoothing parameters are stored in the slot "h" of each element of the list. For example, to get the h-value for the first animal:
kud[[1]]@h
```

4.3 The least square cross validation (LSCV)
```{r}

kudl <- kernelUD(puechabonsp$relocs[,1], h="LSCV")
image(kudl)

#need to look at the LSCV minimization using the plots below due to some unresolved stats issue (look in the package markdown for more info)
plotLSCV(kudl)
```

4.4 Controlling the grid

The UD is estimated at the center of each pixel of a grid. Although the size and resolution of the grid does not have a large effect on the estimates (see Silverman, 1986), it is sometimes useful to be able to control the parameters defining this grid.

4.4.1 Passing a numeric value
```{r}

## The relocations of "Brock"
locs <- puechabonsp$relocs
firs <- locs[as.data.frame(locs)[,1]=="Brock",]

## Graphical parameters
par(mar=c(0,0,2,0))
par(mfrow=c(2,2))

## Estimation of the UD with grid=20 and extent=0.2
image(kernelUD(firs, grid=20, extent=0.2))
title(main="grid=20, extent=0.2")

## Estimation of the UD with grid=20 and extent=0.2
image(kernelUD(firs, grid=80, extent=0.2))
title(main="grid=80, extent=0.2")

## Estimation of the UD with grid=20 and extent=0.2
image(kernelUD(firs, grid=20, extent=3))
title(main="grid=20, extent=3")

## Estimation of the UD with grid=20 and extent=0.2
image(kernelUD(firs, grid=80, extent=3))
title(main="grid=80, extent=3")

#if same$all = TRUE, the same grid is used for all animals, thus for example
kus <- kernelUD(puechabonsp$relocs[,1], same4all=TRUE)
image(kus)
 
#Because all the UD are estimated on the same grid, it is possible to coerce the resulting object as a SpatialPixelsDataFrame:
ii <- estUDm2spixdf(kus)
class(ii)
#This object can then be handed with the functions of the package sp.

```

4.4.2 Passing a SpatialPixelsDataFrame

4.5 Estimating the homerange from the UD

4.5.1 Homeranges in vector mode
function getverticeshr gives you the homerange in a vector mode
```{r}
homerange <- getverticeshr(kudl)
class(homerange)

plot(homerange, col=1:4)
#this can be converted into a shapefile useable in GIS

```

4.5.2 Home ranges in raster mode
function getvolumeUD gives you the homerange in raster mode

```{r}
vud <- getvolumeUD(kudl)
vud
```
To make clear the differences between the output of kernelUD and getvol- umeUD look at the values on the following contourplot:
```{r}
## Set up graphical parameters
par(mfrow=c(2,1))
par(mar=c(0,0,2,0))

## The output of kernelUD for the first animal
image(kudl[[1]])
title("Output of kernelUD")

## Convert into a suitable data structure for
## the use of contour
xyz <- as.image.SpatialGridDataFrame(kudl[[1]])
contour(xyz, add=TRUE)

## and similarly for the output of getvolumeUD
par(mar=c(0,0,2,0))
image(vud[[1]])
title("Output of getvolumeUD")
xyzv <- as.image.SpatialGridDataFrame(vud[[1]])
contour(xyzv, add=TRUE)

```
 
output of kernelUD is the raw data and output of getvolumeUD can be used to compute the homerange (of the first animal)

```{r}
## store the volume under the UD (as computed by getvolumeUD)
## of the first animal in fud
fud <- vud[[1]]

## store the value of the volume under UD in a vector hr95
hr95 <- as.data.frame(fud)[,1]

## if hr95 is <= 95 then the pixel belongs to the home range

## (takes the value 1, 0 otherwise)
25
hr95 <- as.numeric(hr95 <= 95)

## Converts into a data frame
hr95 <- data.frame(hr95)

## Converts to a SpatialPixelsDataFrame
coordinates(hr95) <- coordinates(vud[[1]])
gridded(hr95) <- TRUE

## display the results
image(hr95)
```

4.6 The home range size

```{r}

#getverticeshr contains a column named “area”, which contains the area of the home ranges
as.data.frame(homerange)

#determning home range sizes for different levels of probability
ii <- kernel.area(kudl, percent=seq(50, 95, by=5))
ii
plot(ii)

```


4.7 Taking into account the physical boundary over the study area

Two assumptions need to be made before a boarder can occur:
1. boundary segmenet defined as union of several segements, and each seg length should be at least 3xh (h= smoothing parameter for kernel smoothing)
2. angel between two successive line segments should be greater than pi/2 or lower than -pi/2

```{r}

#used the locator() function to find the boundary and then defined it below boundary
bound <- structure(list(x = c(701751.385381925, 701019.24105475,
                         700739.303517889,
                         700071.760160759, 699522.651915378,
                         698887.40904327, 698510.570051342,
                         698262.932999504, 697843.026694212,
                         698058.363261028),
                         y = c(3161824.03387414,
                          3161824.03387414, 3161446.96718494,
                         3161770.16720425, 3161479.28718687,
                         3161231.50050539, 3161037.5804938,
                         3160294.22044937, 3159389.26039528,
                         3157482.3802813)), .Names = c("x", "y"))
image(puechabonsp$map)
 lines(bound, lwd=3)
 

## convert bound to SpatialLines:
bound <- do.call("cbind",bound)
##Line and Lines functions creates objects of class line or lines from coordinates
Slo1 <- Line(bound)
Sli1 <- Lines(list(Slo1), ID="frontier1")

#use the line/lines created to form a data frame
barrier <- SpatialLines(list(Sli1))

#use this boundary that we created in estimating the utlization distribution
kud <- kernelUD(puechabonsp$relocs[,1], h=100, grid=100, boundary=barrier)
image(kud)
 
```

5. Taking into account the time dependence between relocations
5.1 The brownian bridge kernel method
- This method places a nervel fucntion above each *step* of the trajectory (so there is a line connecting successive relocations)
- This method is implemeneted in the kernelbb()

Two smoothing parameters need to be set:
1. sig1: controlls the width of the "bridges"; larger larger bridge; this is related to the *speed* of the animal
2. sig2: controls the width of the "bumps" added over the relocations; similar to the smoothing parameter in the classic kernel method so its related to the imprecision of the relocations

Example
- boar monitoring at 10 minute intervals
```{r}
data(puechcirc)
x <- puechcirc[1] 
x

plot(x)

```

Previous study showed that mean standard deviation of the relocations (relocations as a sample of the actual position of the animal) is equal to 58 meters on the data we are using
- so we set sig2 = 58 meters

Use the function liker to find the maximum likelihood estiamtion of the parameter sig1

```{r}
lik <- liker(x, sig2 = 58, rangesig1 = c(10, 100))
#the standard deviation range we choose is too large; try again!

lik2 <- liker(x, sig2 = 58, rangesig1 = c(1, 10))
#max = 6.2342

lik2

```
 With these two parameters we can estimate the kernel Brownian bridge home range 
 
```{r}

tata <- kernelbb(x, sig1 = 6.23, sig2 = 58, grid = 50)
tata
#class of this object is estUD, and can be managed as such which we go over in section 4.2

image(tata)
plot(getverticeshr(tata, 95), add=TRUE, lwd=2)

```

5.2 The biases random bridge kernel method

- more realistic in regards to animal movement because points are assigned according to a biased random walk

5.2.2 Implementation
The BRB approach is implemented in the function BRB of adehabitatHR.

**never finsished but skimmed through**
















